Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-10 apples_and_oranges.qmd
Added in code for metaregression excluding wl and cau

# count the number of studies
study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
# CHARLOTTE please check. CB - checked and correct.

@@

# count studies 
study_count_no_wl_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_ids,])
# CHARLOTTE please check
# CB checked and correct

@@

@@

# D. CDRS Sensitivity Analysis ---------------------------------------

@@

#CHARLOTTE please check. CB checked, all good.

>>>>

# count the number of studies
study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
# CHARLOTTE please check. CB - come back to this, possible problem.

@@

# count studies 
study_count_no_wl_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_ids,])
# CHARLOTTE please check
# CB come back to this, possible problem.

@@

# D. Estimate Means and CIs without WL and CAU --------------------------------------- 
# grab the ids for no waitlist and cau
no_wl_or_cau_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl" & df_appl_v_orange$control_type != "cau",]$new_study_id

# use them to loop over the simulated list to subset all the dataframes.
list_no_wl_or_cau <- list()

  list_no_wl_or_cau[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
                                            %in% no_wl_or_cau_ids,]

# count studies 
study_count_no_wl_or_cau_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_or_cau_ids,])
# CHARLOTTE please check

# apply the metareg function to the list of cbt, fluox, esc
list_model_1_no_wl <- run_metaregression(list_no_wl_or_cau , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_no_wl_or_cau <-  aggregate_model_results(list_model_1_no_wl_or_cau, condition)

# now use the function to extract the coefficients
means_no_wl_or_cau <-  lapply(list_model_1_no_wl_or_cau, extract_coefficients_func)

# run the mean function for no wl
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
coef_and_se_means_no_wl_or_cau <- calculate_mean_coefs_ses(means_no_wl_or_cau, condition)
coef_and_se_means_no_wl_or_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_or_cau))

coef_and_se_means_no_wl_or_cau$n <- study_count_no_wl_or_cau_study[study_count_no_wl_or_cau_study$is_missing 
                                                     ==FALSE,]$n

@@

# E. CDRS Sensitivity Analysis ---------------------------------------

@@

#CHARLOTTE please check. CB - come back to this, possible problem.
